---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# protean <img src="man/figures/logo.svg" align="right" height="139" />

<!-- badges: start -->
![r-universe](https://patterninstitute.r-universe.dev/badges/protean)
<!-- badges: end -->

This data package provides protein sequence profiles for OncoKB cancer
genes. These sequence profiles can be useful to infer evolutionary variation at protein
positions which in turn may be used as a proxy for inferring impact of
mutations. The data here provided is mostly useful if used as input to the
AGVGD method: https://cran.r-project.org/package=agvgd.

## Installation

Since `{protean}` is a data package that bundles more than a thousand of
sequence profiles, its size exceeeds CRAN's limits and hence its installation
is provided by Pattern Institute's R-Universe repository:

```r
install.packages("protean", repos = "https://patterninstitute.r-universe.dev")
```

## Usage

To know the genes whose protein sequence profiles are provided use
`exported_genes`:

```{r}
library(protean)

# Number of protein sequence profiles available
length(exported_genes)

# Here are the first 10
exported_genes[1:10]
```

The protein sequence profiles are bundled with `{protean}` and their location
can be found with `profile_path()`:

```{r}
profile_path("TP53")
```

To import one sequence profile into R use `read_profile()`:

```{r}
tp53_prof <- read_profile(profile_path("TP53"))
tp53_prof
```

The column `ortho_profile_seq` contains the ortholog sequences of the profile.
The human sequence is the same across rows and can be found in the column
`human_profile_seq`:

```{r}
tp53_prof[c("ortho_species", "human_profile_seq", "ortho_profile_seq")]
```
