---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# protean <img src="man/figures/logo.svg" align="right" height="139" />

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/protean)](https://CRAN.R-project.org/package=protean)
<!-- badges: end -->

This package provides protein sequence profiles for OncoKB cancer
genes.

These sequence profiles can be useful to infer evolutionary variation at protein
positions which in turn may be used as a proxy for inferring impact of
mutations.

## Installation

```r
install.packages("protean")
```

You can install the development version of `{protean}` like so:

``` r
# install.packages("remotes")
remotes::install_github("maialab/protean")
```

## Usage

To know the genes whose protein sequence profiles are provided use
`exported_genes`:

```{r}
library(protean)

# Number of protein sequence profiles available
length(exported_genes)

# Here's the first 10
exported_genes[1:10]
```

The protein sequence profiles are bundled with `{protean}` and their location
can be found with `profile_path()`:

```{r}
profile_path("TP53")
```

To import one sequence profile into R use `read_profile()`:

```{r}
tp53_prof <- read_profile(profile_path("TP53"))
tp53_prof
```

The column `ortho_profile_seq` contains the ortholog sequences of the profile. The human sequence is the same across rows and can be found in the column `human_profile_seq`:

```{r}
tp53_prof[c("ortho_species", "human_profile_seq", "ortho_profile_seq")]
```
